---
title: "xlio"
output:
  html_document:
    df_print: kable
rmd_output_metadata:
  rsc_output_files:
    - "cbo_tidied.xlsx"
resource_files:
  - "cbo_tidied.xlsx"
---

```{r}
knitr::opts_knit$set(progress = FALSE)
library(tidyverse)
library(tidyxl)
library(unpivotr)
library(readxl)
library(openxlsx)
library(writexl)
library(janitor)
```

Check out this book for more on working with [ms office](https://ardata-fr.github.io/officeverse/)

## get cbo data

```{r}

infile <- "https://www.cbo.gov/system/files/2021-02/51135-2021-02-economicprojections.xlsx"
economic_projections <- basename(infile)

download.file(
  infile,
  economic_projections,
  mode = "wb" # use for files that aren't just plain text
)
```

## readxl

```{r}
readxl::excel_sheets(economic_projections)

quarterly <-
  read_excel(economic_projections, sheet = "1. Quarterly") %>%
  janitor::row_to_names(6) %>% 
  janitor::clean_names() %>%
  fill(
    starts_with("na"), .direction = "down"
  ) %>%
  drop_na(starts_with("x")) %>%
  pivot_longer(
    cols = starts_with("x"),
    names_prefix = "x",
    names_to = c("quarter")
  )
```

## tidyxl + unpivotr

parse spreadsheet in a one-row-per-cell tidy format. Read more at [Spreadsheet Munging Strategies](https://nacnudus.github.io/spreadsheet-munging-strategies/)

```{r}

quarterly_v2 <-
xlsx_cells(economic_projections) %>% 
  filter(
    sheet == "1. Quarterly",
    row > 6, 
    row < 159
    ) %>% 
  select(sheet:character)

```

## write to a database

using the SQLite in-memory database for this example, but see [db.rstudio.com](https://db.rstudio.com/getting-started/) for examples with your preferred database

```{r}
library(DBI)

con <- dbConnect(RSQLite::SQLite(), ":memory:")

dbWriteTable(con, "quarterly_readxl", quarterly)
dbWriteTable(con, "quarterly_tidyxl", quarterly_v2)

dbListTables(con)
dbDisconnect(con)
```

## write to an excel file

```{r}
writexl::write_xlsx(quarterly, "cbo_tidied.xlsx")
```

Check out the [openxlsx docs](https://ycphs.github.io/openxlsx/articles/Formatting.html) for writing sheets with more formatting.

## download data V2

[data](./cbo_tidied.xlsx)
